Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-15 doc/reviews/ResponseToReviewer3.tex

\noindent
\comment{{\bf 1.} In section 2.2, the authors defined a repulsion force with an
empirical formula to prevent particle collisions. However, there is no
benchmark test to show that this artificial repulsion force can generate
correct hydrodynamic lubrication. The authors are suggested to justify
and validate the use of the Imposed Forces with comparison to well-known
lubrication forces between particles.}
\begin{itemize}
  \item Response: The repulsive potential we used to prevent overlap of Janus particles is the repulsive Morse potential based on the electrostatic repulsive potential between two negatively (or positively) charged particles immersed in a medium of low electrolyte concentration so that there is a well-defined zeta potential on the charged particle (Coakley {\sl et al.}, 1999, Biophys. J). This repulsive potential has been approximated by the short-range repulsive Lennard-Jones potential (Flormann {\sl et al.}, 2017, Sci. Reports), which has been adopted by Quaife and Young to study the interaction between two membranes in a viscous solvent in Quaife, Veerapaneni and Young, 2019, Phys. Rev. Fluids, where Quaife {\sl et al.} showed that the lubrication hydrodynamics (draining of fluid between two membrane) is well captured and the scaling of lubrication thin film is recovered.

This is evidence that the lubrication hydrodynamics of the thin film between two particles under the repulsive Morse potential is well captured  if the flow velocity can be accurately calculated in the boundary integral simulations when two particles are sufficiently close to each other and the short-range repulsion is the dominant force.

In this work we used similar numerical techniques to solve the integral equations when some boundaries are quite close to each other.  As the repulsive Morse potential works well to prevent overlapping of particles (provided the time step size is sufficiently small), our previous results in Quaife, Veerapaneni and Young, 2019, Phys. Rev. Fluids gives us confidence in the accuracy of the fluid flow in the thin space between the particles.

\item Change: We added sentences to describe how the lubrication hydrodynamics in a narrow space between boundaries is well-captured within the boundary integral formulation in page 4, starting in line 129.

### 2022-02-15 doc/main_jfm.tex
yny 1st commit

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another (Figure \ref{fig:figure0}a). We then
define the repulsion force and torque
\begin{align}
  \label{eq:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
  \label{eq:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{align}
The repulsion profile $P(r)$ is set to zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
and~\eqref{eq:REPULtorque} ignore particles outside a
$\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
prevent particle collisions. Then, the total imposed force and torque
are
\begin{equation}
\label{eq:total_forces}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{equation}

>>>>

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another (Figure \ref{fig:figure0}a). We then
define the repulsion force and torque
\begin{align}
  \label{eq:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
  \label{eq:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{align}
The repulsion profile $P(r)$ is set to zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
and~\eqref{eq:REPULtorque} ignore particles outside a
$\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
prevent particle collisions. 
\textcolor{magenta}{
The high-order interpolation-based quadrature rule used to compute the nearly-singular integrals has
been shown to well capture the lubrication hydrodynamics in the narrow space between boundaries 
when the repulsive potential $P$ gives a large steric force \cite{qua-bir2014}.  
In the simulations we adjust the spatial resolution on the particle boundary to ensure that the lubrication hydrodynamics is well resolved as in \cite{qua-vee-you2019,qua-gan-you2021}.
}
%
Then, the total imposed force and torque
are
\begin{equation}
\label{eq:total_forces}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{equation}
